Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-01-29 apj.tex
plowing on

The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust laws.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values of the components  vary by $<5$\%.

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\gamma$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors, and a residual vectors perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.82 \\
0.72 & -5.27
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual vectors
\begin{align}
\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\end{align}
contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.
This result indicates that
the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.

To visualize the above result, Figure~\ref{plane:fig} shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$, and close to coplanar in $BVR$.

@@

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and led to the specification of the directions of
the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
can be written as 
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ providing the freedom of choice in the directions of the two basis vectors.  In the analysis,
the arbitrarity is broken and the $\kappa$'s specified, by the  prior of  
zero covariance between $(A^F_V - \kappa_2 E^F(B-V))$ and  $(-\kappa_1 A^F_V + E^F(B-V))$.
The preferred values for $\kappa$ from the linear model in \S\ref{model:sec} are shown qualitatively in
Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
the vector $\gamma^0_X$ is  aligned with 
the dust vector $\left(a(X)+\kappa_1 b(X) \right)$  and $\gamma^1_X$
is aligned with $(\kappa_2 a(X) + b(X))$ for $X=UVI$.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply for  $X=BVR$.

An intuitive understanding of $\kappa_1$ can be obtained by considering what would happen if
all supernovae were to experience dust with the same $R^F$.   The zero-covariance
prior would be satisfied by  $\kappa_1=1/R^F$ and any arbitrary $\kappa_2$.
The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Intrinsically $k_1=0$  and $\gamma^1$ would be unconstrained.
A slight relaxation away from the constant $R^F$ assumption would result in non-zero $k_1$ and a $\gamma^1$ in a direction that satisfies
the prior condition, as parameterized by $\kappa_2$.

Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model ,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$.
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red, consistent
with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.

@@

The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our  supernova
parameters translate to  \citetalias{1999PASP..111...63F} parameters with consistent distributions, lead us to conclude that 
$\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
in standard models of Milky Way dust.  There do remain some small inconsistencies between our numbers and expectations from dust models.
\color{black}

@@

We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
the SED of the SALT2, $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the unextincted
supernova.
The SALT2 SED determines the values of $A_X$ and the
intrinsic colors.

This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections:  the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
Relative to SALT2, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
while simultaneously showing no color excess is $B-R$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
    relative to SALT2.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
allowed by \citetalias{1999PASP..111...63F} dust.
Right:    \label{model1118:fig}}
\end{figure}

@@

The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
and
\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 model,
and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
and there is one global $R$ parameter.

%
%
%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.

The presentation of our results from evaluating this model with SNf data
begins with further evidence of the inconsistency between the ansatz and the models of the previous section.
The current analysis sets the magnitude of an $A_V=0$ supernova, so now  magnitudes in addition to colors of the canonical
supernova in \S\ref{model:sec} can be compared relative to expectations of the dust model.  The magnitude difference
is the difference between the $c_X$ parameters of the two analyses, denoted as $\Delta c_X$.
Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
to SALT2: these values are plotted in
Figure~\ref{model1118:fig}.
The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.

The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram for the median $A_V$ determined for
each supernova. The
$A_V$ distribution  has a slow rise from zero,  compared to the equivalent $\gamma^0_V k_0$
from the linear model of \S\ref{model:sec} that has the sharp rise expected from of a large fraction of supernovae
experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
to $R=3.17^{0.20}_{-0.17}$.

@@

The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models, we therefore
refrain from making absolute conclusions based on our results.  We do emphasize the sensitivity of our results when using the total-to-selective extinction
$R$ parameter.

The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
non-zero.  Insofar that the $A_V$ and $R_V$
parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
is important.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
    \caption{Difference between per-supernova
$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
   \label{CCMF99:fig}}
\end{figure}

>>>>

The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust laws.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values $a$ and $b$ change but only by $<5$\%.

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\gamma$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.82 \\
0.72 & -5.27
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual vectors
\begin{align}
\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\end{align}
contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.
This result indicates that
the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.

The above result is visualized in Figure~\ref{plane:fig}, which  shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$, and close to coplanar in $BVR$.

@@

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
can be written as 
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.  In the analysis,
the $\kappa$'s are specified by the  prior of  
zero covariance between $(A^F_V - \kappa_2 E^F(B-V))$ and  $(-\kappa_1 A^F_V + E^F(B-V))$.
The preferred values for $\kappa$ are shown qualitatively in
Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
the vector $\gamma^0_X$ is  aligned with 
the dust vector $\left(a(X)+\kappa_1 b(X) \right)$  and $\gamma^1_X$
is aligned with $(\kappa_2 a(X) + b(X))$  $UVI$-space.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.

To gain an intuitive understanding of $\kappa_1$, consider the hypothetical case where
all supernovae experience dust with the same $R^F$.   The zero-covariance
prior would be satisfied by  $\kappa_1=1/R^F$ and any arbitrary $\kappa_2$.
The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Both $k_1=0$  and $\gamma^1$ would be unconstrained.
A slight relaxation away from the constant $R^F$ assumption would result in $\kappa_2$ no longer being arbitrary but determined by the prior, and a
non-zero $k_1$ and a $\gamma^1$.

Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$.
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red, consistent
with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.

@@

The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our  supernova
parameters translate to  \citetalias{1999PASP..111...63F} parameters with consistent distributions, lead us to conclude that 
$\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
in standard models of Milky Way dust.  Yet there do remain some small inconsistencies between our numbers and expectations from dust models.
\color{black}

@@

We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
the SED of the SALT2, $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
parameter values of an unextincted
supernova.
The SALT2 SED determines the values of $A_X$ and the
intrinsic colors.

This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
while simultaneously showing no color excess is $B-R$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
allowed by \citetalias{1999PASP..111...63F} dust.
Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
    relative to SALT2. \label{model1118:fig}}
\end{figure}

@@

The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
and
\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
and there is one global $R$ parameter.  
%
%
%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.

Results from evaluating this model with SNf data
provide further evidence of the inconsistency between the ansatz and the models of the previous section.
The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
is the difference between the $c_X$ parameters of the two analyses.
Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
to SALT2: these values are plotted in
Figure~\ref{model1118:fig}.
The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.

The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram for the median $A_V$ determined for
each supernova. The
$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
to $R=3.17^{0.20}_{-0.17}$.

@@

The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
and our ansatz for incorporating dust is limited systematically in measuring 
the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
zero-extinction supernova.

%
%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
%non-zero.  Insofar that the $A_V$ and $R_V$
%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
%is important.
%
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
%    \caption{Difference between per-supernova
%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
%   \label{CCMF99:fig}}
%\end{figure}
